%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\begin{document}
		
\header{ANAND }{KRISHNA SUNIL}{nanduzira@gmail.com | +91-807-806-8096 | Thrissur, Kerala | www.github.com/NaNDuzIRa}
\newline

\section{objective}
\begin{entrylist}

	\entry
	{}
    {{\normalfont To work in a firm with a professional work driven environment where I can utilize and apply my knowledge \& skills which would enable me as a fresher to grow while fulfilling organizational goals.}}
    {\emph{linkedin.com/in/NaNDuzIRa}}
	{}
\end{entrylist}
\newline

\section{education}
\begin{entrylist}
	
	\entry
	{Jun 2014 - Jun 2018}
	{Vidya Academy of Science \& Technology, {\normalfont B.Tech in Computer Science \& Engineering \newline}}
	{Thalakkottukara, Thrissur, Kerala - 680501}
	{\emph{CGPA: Currently Pursuing}}
	  
	
	\entry
	{Jun 2012 - May 2014}
	{I E S Public School, {\normalfont Higher Studies \& Education in Computer Science \& Mathematics \newline}}
	{Chittilappilly Rd, Thrissur, Kerala - 680551}
	{\emph{CGPA: 80.1}}
    
    
	\entry
	{Jun 2011 - May 2012}
	{I E S Public School, {\normalfont All India Secondary School Examination in CBSE 10th \newline }}
	{Chittilappilly Rd, Thrissur, Kerala - 680551}
	{\emph{CGPA: 92}}
	  
\end{entrylist}
\newline

\section{projects}
\begin{entrylist}
	
	\entry
	{Jun 2017 - Apr 2018}
	{Water Classification based on Quality using Machine Learning {\normalfont }}
	{(Ongoing Project)}
	{A platform to evaluate \& predict the quality of water sample by testing the laboratory parameters of the same and classifying it into drinkable, fisheries or others, along with a desktop application for the digitalization of all the future records that they have to maintain.}
	
	
	\entry
	{Jun 2016 - Apr 2017}
	{LED NSS Survey App \& Web-Portal}
	{github.com/nanduzira/lednss.git \newline {Android Studio, PHP, HTML, CSS, MySQL}}
	{An android app that let the volunteers survey and later on upload that data through Internet to a Web-Portal where the data analysis \& the further modifications can be performed on the data.}
	
\end{entrylist}
\newline

\section{skills}
\begin{entrylist}
	\skill{}{Designing Skills: {\normalfont Adobe Photoshop, Adobe Illustrator, Adobe Experience Design.}}
	\skill{}{Programming Skills: {\normalfont C, Java, Python.}}
	\skill{}{Web Development: {\normalfont HTML, CSS, PHP(Laravel), JavaScript.}}
	\skill{}{ERP Development: {\normalfont Basics of Odoo 10.0/Open ERP.}}
	\skill{}{App Development: {\normalfont Android Studio.}}
	\skill{}{Database: {\normalfont MySQL, sqlite3.}}
	\skill{}{Operating Systems: {\normalfont Windows, Linux(Ubuntu, RHEL, Kali).}}
	\skill{}{Other Tools: {\normalfont LaTeX, MS Word, MS Excel, MS Powerpoint.}}
\end{entrylist}
\newline

\newpage

\section{experience}
\begin{entrylist}
	\entry
	{Feb 2018 - Aug 2018}
	{Research Scientist Intern [NLP, Odoo]}
	{Nouveau Labs, Bangalore}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=1pt]
		\item Full-time Internship for a period of six months in areas of NLP and Odoo ERP. Writing programs/modules in Python and training using NLTK and various other NLP Toolkits.
	\end{itemize}}
	\entry
	{10 Oct 2017}
	{DSC Pilot Workshop - I, [Resource Person]}
	{Vidya Academy of Science \& Technology}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=1pt]
		\item Conducted a Workshop on behalf of DSC for students at my college on Basic Android App Development using Android Studio.
		\end{itemize}}
	\entry
	{Jul 2017 – Ongoing}
	{Developers Student Club, [DSC Lead]}
	{Vidya Academy of Science \& Technology}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=1pt]
		\item Guiding \& Managing the Student community at our college to Mobile/Web App Development under the guidance of Google Developer Team.
		\item Conduct Workshops, Sessions, on-take Projects \& Community Works in \& around our College.
		\end{itemize}}
	\entry
	{Dec 2016 – Ongoing}
	{PENTA KTU, [ERP Development]}
	{NSS Technical Cell Kerala}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=1pt]
		\item ERP Development using Odoo 10.0 to manage the work records of all KTU NSS Students in Kerala.
		\end{itemize}}
	\entry
	{Sep 2015 – Sep 2016}
	{PENTA Internship, [Web Development]}
	{NSS Technical Cell, Kerala}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=1pt]
		\item Web Development \& Managing using Joomla CMS Platform.
		\end{itemize}}
\end{entrylist}\newline

\section{trainings}
\begin{entrylist}
	\entry
	{Feb 2018 - Jul 2018}
	{Red Hat Certified Engineer (EX300)}
	{Vidya Academy IT Division \newline \textbf{[Certificate No:170-292-031]}}
	{This exam and the exam objectives provided here are based on the Red  Hat® Enterprise Linux® 7.0 version of the exam.}
	\entry
	{Oct 2017 - Dec 2017}
	{Red Hat Certified System Administrator (EX200)}
	{Vidya Academy IT Division \newline \textbf{[Certificate No:170-292-031]}}
	{Entry-level certification that focuses on actual competencies at system administration.}
	\entry
	{Nov 2017 - Jan 2018}
	{Certified Ethical Hacker (CEHv9)}
	{Vidya Academy IT Division}
	{A methodology that can be used in a penetration testing or ethical hacking situation.}
	\entry
	{Jun 2017 - Jul 2017}
	{Foundation Program - Campus Connect (FP5.0)}
	{Vidya Academy of Science \& Technology}
	{A Training on Python by Infosys.}
	\entry
	{Jul 2016 - Dec 2016}
	{Foundation Program - Campus Connect (FP4.0)}
	{Vidya Academy of Science \& Technology}
	{A Training on Java by Infosys.}
	\entry
	{Oct 2016}
	{mPOWER - Vertical Eye}
	{Vidya Academy of Science \& Technology}
	{A Mind Powering Program for improving our Personality, Communication \& other Leadership Skills.}
    \entry
	{Jul 2016 - Oct 2016}
	{Mobile Computing}
	{NPTEL Online Course}
	{An Android App Development course provided by IIT Delhi.}
    \entry
	{Sep 2016 - Oct 2016}
	{Introduction to Modern Application Development (IMAD)}
	{NPTEL Online Course}
	{A Modern Application Development course provided by IIT Madras.}
    \entry
	{Nov 2016}
	{Web Development using Joomla (CMS)}
	{AXIS College of Engineering}
	{A training program to help and support the development of website for NSS Technical Cell.}
    \entry
	{Jul 2015 - Nov 2015}
	{Infosys Soft Skills Training Program}
	{Vidya Academy of Science \& Technology}
	{A training program to better the peer communication and other basic skills including Leadership Skills.}
\end{entrylist}

\end{document}